Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2015-05-19 Paper/paper.tex
changing figure captions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Systematic bias in recovered parameters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Advanced LIGO searches and parameter estimation efforts aimed at binaries 
containing NS and stellar-mass BHs are poised to use waveform models that do not
include the effects of the NS tidal deformability. While this is not expected to
be the dominant source of error at low SNRs, it will likely introduce a
systematic bias in the physical parameters that we recover from GW observations.
In this section, we study the impact of the same for binaries where the BH spins
are aligned to the orbital angular momentum.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Systematic bias in recovered parameters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[h]
\centering 
\textbf{With BH-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TN_chirpMassBias_vs_SNR_q23.pdf}\\ 
\textbf{With NS-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TT_chirpMassBias_vs_SNR_q23.pdf}%\quad
\caption{These figures show the (fractional) difference between the median value of
recovered posterior distribution for binary chirp mass and the actual injected chirp mass,
as a function of the signal-to-noise-ratio (SNR) of the injected signal.
The top and bottom panels show results for parameter estimation performed using
waveform templates without and with NS matter effects included, respectively.
In each row, the left and right panel correspond to 
$q=m_\mathrm{BH}/m_\mathrm{NS}=\{2,3\}$, respectively. 
In each panel, the color of the curves correspond to the value of NS deformability 
parameter, and line style correspond to the dimensionless spin on the BH 
($\chi_\mathrm{BH}\equiv \dfrac{a}{m_\mathrm{BH}^2}$).
}
\label{fig:TNT_chirpMassBias_vs_SNR_q23}
\end{figure*}
% 
\begin{figure*}[h]
\centering    
\textbf{With BH-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TN_EtaBias_vs_SNR_q23.pdf}\\ 
\textbf{With NS-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TT_EtaBias_vs_SNR_q23.pdf}%\quad
\caption{This figure is similar to Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23},
with the difference that we consider the systematic bias in the dimensionless
mass-ratio $\eta$ here.}
\label{fig:TNT_EtaBias_vs_SNR_q23}
\end{figure*}
% 
\begin{figure*}[h]
\centering    
\textbf{With BH-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TN_BHspinBias_vs_SNR_q23.pdf}\\ 
\textbf{With NS-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TT_BHspinBias_vs_SNR_q23.pdf}%\quad
\caption{This figure is similar to Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23},
with the differences that we consider the systematic bias in the dimensionless
spin on the BH here, and that the differences shown are absolute and not
fractions of the injected spin.}
\label{fig:TNT_BHspinBias_vs_SNR_q23}
\end{figure*}
% 
\begin{figure*}[h]
\centering
\textbf{With NS-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TT_NSLambdaBias_vs_SNR_q23.pdf}
\caption{This figure is similar to the bottom row of
Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23}, with the difference that  we
consider the NS tidal parameter $\Lambda$ here.}
\label{fig:TT_NSLambdaBias_vs_SNR_q23}
\end{figure*}
% 
% 
Advanced LIGO searches and parameter estimation efforts aimed at binaries 
containing NS and stellar-mass BHs are poised to use waveform models that do not
include the effects of the NS tidal deformability. While this is not expected to
be the dominant source of error at low SNRs, it will likely introduce a
systematic bias in the physical parameters that we recover from GW observations.
In this section, we study the impact of the same for binaries where the BH spins
are aligned to the orbital angular momentum.
